### 2017-08-04 paper/incomeShocks-jde-r1.tex
Add file for crop loss and outcomes descriptive statistics

\begin{table}
\centering
\footnotesize
\begin{threeparttable}
\caption{Descriptive statistics for Crop loss and Outcomes}
\label{tab:desc_stat_croploss}
\begin{tabular}{l  D{.}{.}{2,3} D{.}{.}{2,3} D{.}{.}{2,3} D{.}{.}{2,3} D{.}{.}{2,3}} \toprule
                                  & \multicolumn{4}{c}{Wave} & \mco{Average} \\ \cmidrule(lr){2-5}
                                  &\multicolumn{1}{c}{1} &\multicolumn{1}{c}{2}   &\multicolumn{1}{c}{3} &\multicolumn{1}{c}{4} &   \\ \midrule
Dummy crop loss (1-7 months) $\geq$ TZS 200            &        0.71&        0.26&        0.02&        0.03&        0.25\\
                                                       &      (0.45)&      (0.44)&      (0.13)&      (0.18)&      (0.44)\\ 
\addlinespace 
Currently pregnant                                     &        0.17&        0.23&        0.15&        0.14&        0.17\\
                                                       &      (0.37)&      (0.42)&      (0.36)&      (0.35)&      (0.38)\\
Gave birth since last survey                           &        0.19&        0.16&        0.22&        0.12&        0.17\\
                                                       &      (0.40)&      (0.37)&      (0.41)&      (0.32)&      (0.38)\\
\addlinespace 
Contraceptive use                                      &        0.15&        0.09&        0.09&        0.10&        0.11\\
                                                       &      (0.36)&      (0.29)&      (0.29)&      (0.30)&      (0.31)\\
Contraceptive use -- Traditional\tnote{a}              &        0.11&        0.06&        0.07&        0.04&        0.07\\
                                                       &      (0.32)&      (0.24)&      (0.25)&      (0.21)&      (0.26)\\
Contraceptive use -- Modern\tnote{b}                   &        0.04&        0.02&        0.02&        0.05&        0.03\\
                                                       &      (0.20)&      (0.14)&      (0.14)&      (0.22)&      (0.18)\\ 
\bottomrule
\end{tabular}
\begin{tablenotes} 
\scriptsize
\item[a] Traditional contraceptives include abstinence and rhythm method.
\item[b] Modern contraceptives include condom, diaphragm, pill, IUD, injection, female and 
male sterilization.
\end{tablenotes}
\end{threeparttable}
\end{table}

>>>>

% Descriptive statistics by wave
\input{../tables/desstat2.tex}
